Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:14	17:04:42	(Fri14.Aug)

Synnev\aa{}g used a window set comprised of rectangular, Kaiser and inverted Kaiser functions. Of these only a specific Kaiser window were steered We limit our study to the use of variations of the parametric Kaiser-Harris window, since we observed neglible performance difference to using this function or any of the common trigonometric ones. The Kaiser windows are easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

@@

>>>>

Synnev\aa{}g used a window set comprised of rectangular, Kaiser and inverted Kaiser functions. Of these a specific Kaiser window were micro-steered. We limit our study to the use of variations of the parametric Kaiser-Harris window, since we observed neglible performance difference to using this function or any of the common trigonometric ones. The Kaiser windows are easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

@@

\subsection{Relative steering}
